The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2018-05-01 script/en/chapters/introduction.tex
CT1: Updated CT book (d+e): typos, dead links, 2018, 50th M-prime, automated rowno in 2 tables in chap 3, Make.rules also for Windows
CT1: Updated CT book (e): \phantomsection, \addcontentsline, and \chapter* substituted (hint from Brian Dunn)

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Preface to the 12th Edition of the CrypTool Book}
\chapter*{Preface to the 12th Edition of the CrypTool Book}

@@

\par \vskip + 35pt
\noindent Bernhard Esslinger
\par \vskip + 10pt
\noindent Heilbronn/Siegen (Germany), August 2016 + August 2017

@@

\par \vskip + 15pt
\noindent PPS:\\%xxxxxxxxxx Todo
Todos to be dealt with to make edition 12 of this CTB a release (till then we still call it a draft):%xxxxxxxxxxxxx
\begin{compactitem}
   \item Update all information about SageMath (chap.~\ref{ec:Sage_Massierer}
      and appendix) and run the code against the newest SageMath (version 8.x) -- 
      both command line and SageMathCloud notebook.
   \item Update the function lists of the four CT versions (in the appendix).
\end{compactitem}

% --------------------------------------------------------------------------
\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Introduction -- How do the Book and the Programs Play together?}
\chapter*{Introduction -- How do the Book and the Programs Play together?}

>>>>

\clearpage
\setcounter{secnumdepth}{-1}  % Prevent this chapter title from having a number
\chapter{Preface to the 12th Edition of the CrypTool Book}
\setcounter{secnumdepth}{4}  % Set back default from CT-Book-en.tex (show numbers till level 4)

@@

\par \vskip + 35pt
\noindent Bernhard Esslinger
\par \vskip + 10pt
\noindent Heilbronn/Siegen (Germany), August 2016 + August 2017 + April 2018

@@

\par \vskip + 15pt
\noindent PPS:\\%xxxxxxxxxx Todo
Todos to be dealt with to make edition 12 of this CTB a release (till then we still call it a draft):%xxxxxxxxxxxxx
\begin{compactitem}
   \item Update all information about SageMath (chap.~\ref{ec:Sage_Massierer}
      and appendix) and run the code against the newest SageMath (version 8.x) --
      both command line and SageMathCloud notebook. SageMath 8 is also
      available for Windows.
   \item Update the function lists of the four CT versions (in the appendix).
\end{compactitem}

% --------------------------------------------------------------------------
% BE_2018-05-02: According to Brian Dunn's recommendation: \phantomsection and
%                \chapter* substituted by \chapter and setting/resetting secnumdepth.
%                This also allows to get rid of \addcontentsline
% \clearpage\phantomsection
% \addcontentsline{toc}{chapter}{Introduction -- How do the Book and the Programs Play together?}
% \chapter*{Introduction -- How do the Book and the Programs Play together?}

\clearpage
\setcounter{secnumdepth}{-1}  % Prevent this chapter title from having a number
\chapter{Introduction -- How do the Book and the Programs Play together?}
\setcounter{secnumdepth}{4}  % Set back default from CT-Book-en.tex (show numbers till level 4)

### 2018-05-01 script/en/chapters/overviewcontent.tex
CT1: Updated CT book (e): \phantomsection, \addcontentsline, and \chapter* substituted (hint from Brian Dunn)

\clearpage\phantomsection

\addcontentsline{toc}{chapter}{Overview about the Content of the CrypTool Book}
\chapter*{Overview about the Content of the CrypTool Book}

>>>>

\clearpage
\setcounter{secnumdepth}{-1}  % Prevent this chapter title from having a number
\chapter{Overview about the Content of the CrypTool Book}
\setcounter{secnumdepth}{4}  % Set back default from CT-Book-en.tex (show numbers till level 4)
